---
title: "Linear Model with Prediction"
author: "Thomas Matthews"
date: "4/8/2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# simple regression

This is a template to serve as an example (cut and paste, change variable names)  
we use the ucdavis1 dataset from the tigerstats package.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```


```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

# SIMS~ARM

## Scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```  

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

### Linear Model
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The line equation is SIMS = -4.1 + 0.05 * ARM.
The model suggests that r-squared is .467 and another metric is the residual standard error, is 1.226.

### Prediction

```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.1, new, interval = "prediction", level = .95)
```

# SIMS~GRIP

### Scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN +  geom_point() + geom_smooth(method=lm)
```

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

### Linear Model
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The line equation is SIMS = -4.81 + 0.05 * GRIP
The model suggests that r-squared is .467 and another metric is the residual standard error, is 1.295.

### Prediction

```{r}
predict(model.2, new, interval = "prediction", level = .95)
```

# SIMS~ARM+GRIP

### Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

### Linear Model
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The line equation is SIMS = -5.4 + 0.04 * GRIP.
The model suggests that r-squared is 0.536 and another metric is the residual standard error, is 1.144. This model is better than the previous two, because its residual standard error is smaller and the adjusted is bigger than both. 

### Prediction

```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.3, new, interval = "prediction", level = .95)
```

# Compare Model1 with Model3

### ANOVA

### Model1 vs Model3

```{r}
anova(model.1,model.2)
```



### Model1 vs Model3

```{r}
anova(model.1,model.3)
```

The p-value, which is 0.000004, is very low. So, that means there is a significant difference between the two models. That difference is 29.45. Is better than the model with just ARM. 

### Model2 vs SIMS~ARM+GRIP

```{r}
anova(model.2,model.3)
```

The p-value is smaller than the previous and is very significant. The difference between the two models is 54, yet another significant result. 





