---
title: "Linear Model with Prediction"
author: "Thomas Matthews"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# simple regression

This is a template to serve as an example (cut and paste, change variable names)  
we use the ucdavis1 dataset from the tigerstats package.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```

## R Markdown

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

Then issue

data <- read.csv(file="paste link here",sep="",header=TRUE)  

that sep=""  in the command is needed since the file is space delimited, not comma separated.  The header=TRUE is also necessary so that the names of the variables and their formats get correctly imported.

New aspects of this assignment

You need to create your Rmarkdown file without a starting template
You need to create a new github repo from scratch

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

# SIMS~ARM

## Scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```  

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

### Linear Model
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The line equation is SIMS = -4.1 + 0.05 * ARM.
The model suggests that r-squared is .467 and another metric is the residual standard error, is 1.226.

### Prediction

```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.1, new, interval = "prediction", level = .95)
```




# SIMS~GRIP

### Scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN +  geom_point() + geom_smooth(method=lm)
```

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

### Linear Model
  
```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```


# SIMS~ARM+GRIP






# Compare Model1 with Model3















